\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-24 icse20/conclusion.tex
Updated final numbers

\section{Conclusion}\label{sec:conclude}
The annual updates of the ECMAScript specification makes it difficult to
build program analysis or formal verification of JavaScript due to the
required human efforts in modeling a moving target.  In this paper,
we proposed a tool \( \tool \), which \textit{automatically} extracts the
syntax and semantics specified in the ECMAScript specification.  The tool
generates a parser from a language grammar written in \( \bnfes \), and
compiles abstract algorithms written in English to \( \ires \) functions.
The only parts that require manual efforts are compile rules and
language-specific global setting, which we provide for ECMAScript
as an example case study.  We also support a rule assistant to guide
how to convert new abstract algorithms.  We evaluated \( \tool \) by
applying it to ECMAScript 2020 with Test262.  The extracted semantics
passed all \inred{XXXXX} applicable tests in Test262 and we showed
that the tool is also applicable to an incomplete language proposal as
a case study.  The tool also detected six confirmed errors from the
specification and the proposal. The implementation of the tool is
publicly available as an open-source project.

>>>>

\section{Conclusion}\label{sec:conclude}
The annual updates of the ECMAScript specification makes it difficult to
build program analysis or formal verification of JavaScript due to the
required human efforts in modeling a moving target.  In this paper,
we proposed a tool \( \tool \), which \textit{automatically} extracts the
syntax and semantics specified in the ECMAScript specification.  The tool
generates a parser from a language grammar written in \( \bnfes \), and
compiles abstract algorithms written in English to \( \ires \) functions.
The only parts that require manual efforts are compile rules and
language-specific global setting, which we provide for ECMAScript
as an example case study.  We also support a rule assistant to guide
how to convert new abstract algorithms.  We evaluated \( \tool \) by
applying it to ECMAScript 2020 with Test262.  The extracted semantics
passed 19,220 of 19,282 applicable tests in Test262 and we showed
that the tool is also applicable to an incomplete language proposal as
a case study.  The tool also detected six confirmed errors from the
specification and the proposal. The implementation of the tool is
publicly available as an open-source project.

### 2019-08-24 icse20/eval.tex
Updated final numbers

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
\vspace*{-.5em}
\small
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,895\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,125}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,136\\\hdashline
    Module tests& 918 \\\hdashline
    Inessential built-in object tests & \inred{XXXX}\\\hdashline
    Non-standard negative tests & 2,280\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{\inred{XXXXX}}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & \inred{XXXX} \\\hdashline
    Failed tests & \inred{XXXX} \\\bottomrule
  \end{tabular}
\vspace*{-1em}
\end{table}

@@

We tested the interpreter using Test262, the official conformance test
suite provided by TC39, as of August 6, 2019.  Because Test262
contains tests for extensions and in-progress features, we excluded
them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
Test262 consists of 36,794 tests and we excluded 7,669 tests for
extensions and in-progress features.  We also excluded \inred{XXXX}
tests for excluded features and non-standard negative tests.
Finally, we tested \inred{XXXXX} applicable tests with our JavaScript
interpreter and they all successfully passed, which means that all the
semantics extracted from \( \tool \) are perfectly correct.

>>>>

\subsection{Correctness}
\begin{table}[t]
  \centering
  \caption{Testing results of Test262 for ECMAScript 2020}
  \label{table:test262}
\vspace*{-.5em}
\small
  \begin{tabular}{lr}\toprule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{All tests262 Tests} & \textbf{36,794}\\
    \aboverulesepcolor{gainsboro}\midrule
    Annexes/Internationalisation & 1,774\\\hdashline
    In-progress features & 5,895\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{ECMAScript 2020 Tests} & \textbf{29,125}\\
    \aboverulesepcolor{gainsboro}\midrule
    Non-strict mode tests & 1,136\\\hdashline
    Module tests& 918 \\\hdashline
    Early error tests & 1,316\\\hdashline
    Inessential built-in object tests & 6,473\\\midrule
    \belowrulesepcolor{gainsboro}
    \rowcolor{gainsboro} \textbf{Applicable Tests} & \textbf{19,282}\\
    \aboverulesepcolor{gainsboro}\midrule
    Passed tests & 19,220 \\\hdashline
    Failed tests & 62 \\\bottomrule
  \end{tabular}
\vspace*{-1em}
\end{table}

@@

We tested the interpreter using Test262, the official conformance test
suite provided by TC39, as of August 6, 2019.  Because Test262
contains tests for extensions and in-progress features, we excluded
them to focus on the semantics of ECMAScript 2020.  As Table~\ref{table:test262} shows,
Test262 consists of 36,794 tests and we excluded 7,669 tests for
extensions and in-progress features.  We also filtered out
tests for excluded features described in Section~\ref{sec:impl}.
Finally, we tested 19,282 applicable tests with our JavaScript
interpreter and only 62 tests are failed. Among them, 54 tests
utilize implementation-dependent features and 3 tests are timeout
and 5 tests are wrong tests. Thus, we believe that all the
semantics extracted from \( \tool \) are correct.

### 2019-08-24 icse20/impl.tex
Updated final numbers

>>>>

\paragraph{Early Errors}
ECMAScript specifications declare their syntax not only using
\( \bnfes \) but also using Early Error Rule to violate invalid codes
before evaluations. For example, an Early Error Rule checks whether
functions have duplicated parameters in strict mode. However,
there are written in natural languages with differenet styles
with abstract algorithms. Thus, we do not support Early Error Rules.

### 2019-08-24 icse20/intro.tex
Updated final numbers

The main contribution of this paper is \( \tool \):
\begin{itemize}[leftmargin=0.5cm]
\item We successfully applied \( \tool \) to ECMAScript 2020, the next
ECMAScript version scheduled to be released in June 2020.  The
automatically extracted semantics passed the official conformance test
suite, Test262~\cite{test262}; out of \inred{XXXXX} tests for
ECMAScript 2020 it passed \inred{XXXXX} tests.
\item \( \tool \) is also applicable to new language features proposed
for a future release to aid language development in a modular way.
Because ECMAScript is an open standard language, various proposals are
available with their own specification changes and tests.  As a case
study, we applied \( \tool \) to such a proposal, during which the tool
found some errors in the proposal.  The reported errors were all confirmed
and the tool passed all the tests.
\item Moreover, since the extraction mechanism of \( \tool \) is fully
automatic, we can use it to find possible specification errors.  We
indeed found 3 specification errors in ECMAScript 2020.  They were all
confirmed by TC39 and will be fixed in the next release.
\end{itemize}

>>>>

The main contribution of this paper is \( \tool \):
\begin{itemize}[leftmargin=0.5cm]
\item We successfully applied \( \tool \) to ECMAScript 2020, the next
ECMAScript version scheduled to be released in June 2020.  The
automatically extracted semantics passed the official conformance test
suite, Test262~\cite{test262}; out of 19,282 tests for
ECMAScript 2020 it passed 19,220 tests.
\item \( \tool \) is also applicable to new language features proposed
for a future release to aid language development in a modular way.
Because ECMAScript is an open standard language, various proposals are
available with their own specification changes and tests.  As a case
study, we applied \( \tool \) to such a proposal, during which the tool
found some errors in the proposal.  The reported errors were all confirmed
and the tool passed all the tests.
\item Moreover, since the extraction mechanism of \( \tool \) is fully
automatic, we can use it to find possible specification errors.  We
indeed found 3 specification errors in ECMAScript 2020.  They were all
confirmed by TC39 and will be fixed in the next release.
\end{itemize}

### 2019-08-24 icse20/main.tex
Renamed directory icse -> icse20
Updated final numbers

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain.  It \textit{automatically} extracts the JavaScript syntax and
semantics from ECMAScript specifications.  \( \tool \) generates a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript specifications.  It also converts each
abstract algorithm written in a structured natural language into
functions written in \( \ires \), an Intermediate Representation
for ECMAScript specifications.  The compilation from algorithms to
\( \ires \) functions is defined with \textit{compile rules}.
We applied \( \tool \) to ECMAScript 2020,
and the automatically extracted semantics passed all \inred{XXXXX}
applicable tests in Test262, the official ECMAScript conformance test
suite.  The tool also extracted the semantics of an incomplete proposal,
and it detected three errors from the specification and they were all
confirmed.
\end{abstract}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{ref}

>>>>

To alleviate the problem, we propose \( \tool \), a JavaScript IR-based Semantics
Extraction Toolchain.  It \textit{automatically} extracts the JavaScript syntax and
semantics from ECMAScript specifications.  \( \tool \) generates a JavaScript
parser for a given grammar written in \( \bnfes \), an extended BNF
used in ECMAScript specifications.  It also converts each
abstract algorithm written in a structured natural language into
functions written in \( \ires \), an Intermediate Representation
for ECMAScript specifications.  The compilation from algorithms to
\( \ires \) functions is defined with \textit{compile rules}.
We applied \( \tool \) to ECMAScript 2020,
and the automatically extracted semantics passed 19,220 of 19,282
applicable tests in Test262, the official ECMAScript conformance test
suite.  The tool also extracted the semantics of an incomplete proposal,
and it detected three errors from the specification and they were all
confirmed.
\end{abstract}

@@

\normalem
\bibliographystyle{ACM-Reference-Format}
\bibliography{ref}
